\subsection{Sinusoid}
The sinusoid waveform or \textit{sine wave} is the fundamental type of alternating current (ac) or alternating voltage. It is also reffered to as a sinusoidal wave, or simply sinusoid. In addition, other types of repetitive \textit{waveforms} are composites of many individual sine waves called harmonics.
\newline \textit{Sinusoids} are produced by two types of sources: \begin{itemize}
    \item Rotating electrical machines (ac generator)
    \item Electronic oscillator circuits, which are used in instruments commonly known as electronic signal generators
\end{itemize} 
\subsubsection{Amplitude}
The maximum value of a voltage or current.

\subsubsection{Frequency \& Period}
\textit{Frequency} is the number of cycles that a sinusoid completes in one second. The more cycles completed in one second, the higher the frequency. Frequency (f) is measured in unites of hertz (Hz).
\newline 

A \textit{sinusoid} varies with time (\textit{t}) in a definable manner. The time required for a given sinusoid to complete one full cycle is called the period(\textit{T}). 

The formulas for the relationship between frequency and period are
\[f = \frac{1}{T}\] 

\[T = \frac{1}{f}\]


\subsubsection{Phase shift}
The phase of a sinusoid is an angular measurement that specifies the position of that sinusoid relative to a reference. When a sinusoid is shifted to the right of the reference (lags) by a certain angle, \textbf{$\phi$}. 

\[y = A\, sin(\theta-\phi)\] 

\subsection{Square wave}

A \textit{Square wave} is a pulse waveform with a duty cycle of 50\%.
\subsubsection{Pulse width \& Duty Cycle}
\textit{Pulse width} is the time between the point on the leading edge where the value is 50 \% of the amplitued and the point on the trailing edge where the value is 50\% of the amplitude. 

\subsubsection{Rise \& fall time}
\textit{Rise time} is the time required for the pulse to go from 10\% of its amplitued to 90\% of its amplitude. 
\newline \textit{Fall time} is the time required for the pulse to go from 90\% of its amplitued to 10\% of its amplitude.
